---
title: "Base R- Weekly Assignment #2"
author: "Amanda Mae Woodward"
date: "2023-10-03"
output: html_document
---
# Set Up
1. Load the tidyverse library. 
```{r}
library(tidyverse)
```
2. Load the billboard data. 
```{r}
data(billboard)
```
3. What type of data is this? (e.g. describe what's in the dataset).

the dataset includes the top 100 songs from the 2000's 
                               
4. Print the column names from this dataset. 
```{r}
colnames(billboard)
```
5. Print the first 5 entries in the dataset. 
```{r}
head(billboard, n=5)
```
# Practice
1. Create a subset of data that has Jay-Z as the only artist. How many songs are in it?
```{r}
jayZ<- billboard %>% filter(artist=="Jay-Z")
```
5 songs in this dataset
2. In the original dataset, use filter to find information about the song "All the small things." What was the highest position this song reached on the billboard 100? 
```{r}
billboard %>% filter(track=="All The Small Things")
```
in week 12, it was rated #6
                               
3. Create a subset of data for songs Tim McGraw sang. Summarize the data for wk 1.
```{r} 
timMc<- subset(billboard, billboard$artist=="McGraw, Tim")                              
summary(timMc$wk1)
```
4. Create a function that can be used to determine if Britney Spears sang the song. 
```{r}
isBritney<- function(name){
  ifelse(name == "Spears, Britney", "it's Britney", "it's not Britney")
}
```
5. Test your function on the billboard data. Save the results to a new column called "wasItBritney"
```{r}
billboard$wasItBritney<- isBritney(billboard$artist)
```
6. Use a for loop to determine if a song placed 50 or below or placed above 50 during the first week. 
```{r}
billboard$weekOneHalf<-NA
for(i in 1:nrow(billboard)){
  if(billboard$wk1[i]> 50){
  billboard$weekOneHalf[i]<- "above 50"
  } else{billboard$weekOneHalf[i]<- "below 50"}
```
7. Use an if else statement to determine the same information as you obtained with the for loop. 
```{r}
billboard$weekOneHalfB<- ifelse(billboard$wk1>50, "higher", "lower")
```
8. Compare your results. 
They are the same, just in different columns
