---
title: "Quiz 2"
author: "Amanda Mae Woodward"
date: "2023-10-11"
output: html_document
---
This quiz will focus on data frame manipulation, however, you may need to rely on skills you've learned in prior weeks. 

1. load the starwars dataset from tidyverse
```{r}
library(tidyverse)
data(starwars)
```

2. separate the films column so that there is one film in each column (don't worry about the "c(" and ) at the end for now)
```{r}
starwars2<- starwars %>% separate(films, into = c("film1","film2","film3", "film4","film5", "film6","film7"), sep = ",")

```

3. alter the data from wide data to long data
```{r}
starwarsLong<- pivot_longer(starwars2, cols =c("film1", "film2", "film3", "film4","film5", "film6","film7"),names_to="filmNumber", values_to= "filmName" )
```

4. in the column where you stored the films, rename the levels so each film name is consistent (e.g. get rid of the "c(" and ")" )
```{r}
starwarsLong$filmName<- as.factor(starwarsLong$filmName)
levels(starwarsLong$filmName)<- c()
```

5. Create a column in your dataset that indicates whether a character was in the first starwars film, *Star Wars Episode IV: A New Hope* 

6. BMI is calculated as mass in Kg/height in meters. You currently have mass in Kg and height in cm. Create a column that contains each character's BMI. 

7. create a dataframe that contains only the name, hair color, and eye color for each character. 
